Learning to Group and Order AMR Semantics for General Purpose Discourse Planning

### 2015-12-10 paper/paper.tex
add numbers for mean sentence info

>>>>

Looking at table \ref{tab:metrics}, we also see that the optimized pipeline
prefers fewer sentences per paragraph, with marginally more information per
sentence, than the baseline.

\begin{table}[H]
\centering
\caption{Mean number of sentences and facts per sentence for the pipeline}
\label{tab:metrics}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean \# of Sentences} & \textbf{Mean \#
of Facts per Sentence} \\ \midrule
Baseline, Baseline & 6.1074766355140184 & 2.3297628156082633 \\
Greedy, Greedy & 5.8130841121495331 & 2.447749196141479 \\
Greedy, Annealing & 5.8130841121495331 & 2.447749196141479 \\ \bottomrule
\end{tabular}
\end{table}
